Carbonate chemistry at Ny-Ålesund

### 2022-03-29 awipev-CO2.Rmd
Reorganized variable names

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
  dplyr::rename(pressure = depth,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                t_11m = temp_insitu_11m,
                t_ctd = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_s = temp_fb,
                t_sf = temp_sf, 
                at = at, 
                at_calc = at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_fb,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                pH_dur = pH_dur,
                ph_calc = ph_calc_fb
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# t_11m = temperature in situ at 11 m
# t_ctd = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
```

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="Measured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = size_labs)

# SEAFET pH
ts_pH <- d_all %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf, col = depth), alpha = alpha, na.rm = TRUE, size = size_point) + 
  scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors
  guides(colour = guide_colourbar(reverse = TRUE)) + # reverse colour bar
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="In situ pH, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm'))

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
  Mytheme(size_labs = size_labs)

# Combine plots
g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
rm(list = ls(pattern = "ts_")) #delete big ggplot objects
gc() #garbage collection

>>>>

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
  dplyr::rename(pressure = depth,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                t_11m = temp_insitu_11m,
                t_ctd = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_s = temp_fb,
                t_sf = temp_sf, 
                at = at, 
                at_calc = at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_fb_insi_temp,
                pco2_calc = pco2_calc_fb_insi_temp,
                pH_sf = pHint_tot_sf,
                pH_dur = pH_dur,
                ph_calc = ph_calc_fb
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# t_11m = temperature in situ at 11 m
# t_ctd = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature 
# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature
# pco2 = pCO2 in Ferrybox expressed at in situ temperature
# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
# pH_sf = pH seaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
```

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="pCO2 at in situ temperature (measured in blue; calculated from CT and AT in red)",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = size_labs)

# SEAFET pH
ts_pH <- d_all %>% 
  dplyr::filter(depth > 8) %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="In situ pH below 8 m at in situ temperature (seaFET in blue; spectrophotometric in red)", x = "", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm'))

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="Total alkalinity (calculated from salinity in blue; discrete measurements in red)", x="", y="AT (umol/kg)") +
  Mytheme(size_labs = size_labs)

# Combine plots
g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
rm(list = ls(pattern = "ts_")) #delete big ggplot objects
gc() #garbage collection
